\textbf{EECS 340: Assignment 7}

### 2020-04-28 assignment_7/article.tex
✨ Add Problem 2(b) response.
🔨 Add setup description for Problem 2.
✨ Add Henry's response to Problem 4.
✨ Add Yuhui's response to Problem 4.
🐛 Fix incorrect Problem 2(a) due to misread of uv being an edge.

@@

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{{fig/fig_2_a.png}}
\end{figure}

Note the tuple below each node represents their \ilc{(start-time, finish-time)}. It is shown that $v.f > u.f$ as $6 > 4$, however there is no circle between $uv$. Thus, this conterexample disproves the statement.

@@

>>>>

Note the tuple below each node represents their \ilc{(start-time, finish-time)}.

@@

Proof with cases:

There are two possible cases where we can have a $v.f > u.f$:

\begin{itemize}
    \item Case 1: $v.d < u.d < u.f < v.f$\newline
    In this case $u$ is a decent of $v$, which means there must be a path of $v \rightarrow u$; and known that we have $uv \in E$ (from the question instruction), this implies there is a direct connection of $u \rightarrow v$. Thus, now we have a path of $v \rightarrow u$ and a path of $u \rightarrow v$, $uv$ is guaranteed to be on a circle.
    \item Case 2: $u.d < u.f < v.d < v.f$\newline
    In this case we have $u$ completely discovered before $v$. This suggest there shoule be no relationship between $u$ and $v$, as $v$ should not be a decendent nor ancestor of $u$. However, it is known from the question that we have $uv \in E$, which implies $v$ must be a decendent of $u$. Thus, this case will not be valid under the question restriction and therefore disregarded.
\end{itemize}

As all legal case(s) shows $uv$ is guaranteed to be on a circle, we may prove the statement to be true.

\subsection{(b)}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.35\linewidth]{{fig/fig_2_b.png}}
\end{figure}

It is shown that there is a path from $v$ to $u$ as $v \rightarrow a \rightarrow u$, however $uv$ is still a cross edge as $v.d < v.f < u.d < u.f$ ($2 < 3 < 4 < 5$). Thus, this conterexample disproves the statement.

@@

\subsection{Shaochen (Henry) ZHONG's proof of course evalution}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{{fig/fig_4_a.png}}
\end{figure}

\subsection{Yuhui ZHANG's proof of course evalution}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.7\linewidth]{{fig/fig_4_b.png}}
\end{figure}
